Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Added comments on candidates and final round candidates

\subsection{The candidates}
If we look primarily at the large file up/download we see that the candidates
that outperforms, or are close to outperforming \ac{SHA}-256 are BLAKE,
\ac{BMW}, Shabal, Simd and Luffa.

\subsection{Final round candidates}
BLAKE, Keccak, Skein, Grøstl and JH have made it through to the final round of
the \ac{SHA}-3 competition. %TODO: some comments on theese

>>>>

\subsection{The candidates}
If we look primarily at the large file up/download we see that the candidates
that outperforms, or are close to outperforming \ac{SHA}-256 are BLAKE,
\ac{BMW}, Shabal, Simd and Luffa. The same is true if we eliminate the overhead
cause by our bindings for the small files. That only these five candidates
manages to outperform is expected from the \ac{SUPERCOP} results, REF, however
the order and proportion of the measurements does not. This is primarily
because we have not used the fastest implementation for all candidates, and the
relative speed of the chosen implementation compared to the fastest
implementation in \ac{SUPERCOP} differs (Table \ref{tbl:sha3:relativespeed}.
The performance of each candidate compared to the \ac{SHA}-256 version found in
Tahoe-\ac{LAFS} is also somewhat slower than you would expect. We blame this
mainly on our Cython-bindings and our skill. We believe a developer with more
knowledge of the inner workings of the implementations, the Python C-\ac{API}
and \ac{GCC} could have produced better results.

\subsection{Final round candidates}
BLAKE, Keccak, Skein, Grøstl and JH have made it through to the final round of
the \ac{SHA}-3 competition. From a performance perspective only BLAKE actually
outperform \ac{SHA}-256 in both the \ac{SUPERCOP} results and our measurements
for Tahoe-\ac{LAFS}. The other candidates are perhaps given an unfair treatment
in this paper, with the implementations measures being relatively slow compared
to the best implementations. However the reason for this is mentioned in our
criteria for selecting implementations. Another obvious reason is that none of
the other four finalists outperform \ac{SHA}-256 and therefore it would be more
valuable for Tahoe-\ac{LAFS} to see the possible performance increase by
switching to a faster hash function implementation.
